### 2014-04-24 presentation/tilePlacement/step8.tex

		%first 
		\node[align=center, rounded corners, box, draw] at (7,.5) {9\\12};
		% \node[align=center] at (8.5,.5) {1.5};
		\node[align=center, rounded corners, box, draw] at (14,.5) {11\\13};
		% \node[align=center] at (15.5,.5) {0.5};
		\draw (10.5,2) -- (7,1.5);
		\draw (10.5,2) -- (14,1.5);

		%right side row 2
		\node[align=center, rounded corners, box, draw] at (12.5,-2) {13\\9};
		% \node[align=center] at (14,-2) {1.0};
		\draw (14,-.5) -- (12.5,-1);
		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-2) {12\\9.2};
		\node[align=center] at (17,-2) {1.8};
		\draw (14,-.5) -- (15.5,-1);

		% left side row 2
		\draw (7,-.5) -- (5.5,-1);
		\draw (7,-.5) -- (8.5,-1);
		\node[align=center, rounded corners, box, draw, fill = orange] at (5.5,-2) {13\\9};
		\node[align=center] at (7,-2) {3.0};
		\node[align=center, rounded corners, box, draw, fill = green] at (8.5,-2) {12\\9.2};
		\node[align=center] at (10,-2) {1.8};

		% left side row 3
		\node[align=center, rounded corners, box, draw, fill = orange] at (8.5,-4.5) {11\\13};
		\node[align=center] at (10,-4.5) {5.2};
		\draw (8.5,-3) -- (8.5,-3.5);

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, box, draw] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {1.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, box, draw, fill = orange] at (12.5,-7) {12\\9.2};
		\node[align=center] at (14,-7) {2.0};

>>>>

		%first 
		\node[align=center, rounded corners, draw] at (7,.5) {9\\12};
		% \node[align=center] at (8.5,.5) {1.5};
		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
		% \node[align=center] at (15.5,.5) {0.5};
		\draw (10.5,2) -- (7,1.5);
		\draw (10.5,2) -- (14,1.5);

		%right side row 2
		\node[align=center, rounded corners, draw] at (12.5,-2) {13\\9};
		% \node[align=center] at (14,-2) {1.0};
		\draw (14,-.5) -- (12.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-2) {12\\9.2};
		\node[align=center] at (17,-2) {1.8};
		\draw (14,-.5) -- (15.5,-1);

		% left side row 2
		\draw (7,-.5) -- (5.5,-1);
		\draw (7,-.5) -- (8.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
		\node[align=center] at (7,-2) {3.0};
		\node[align=center, rounded corners, draw, fill = green] at (8.5,-2) {12\\9.2};
		\node[align=center] at (10,-2) {1.8};

		% left side row 3
		\node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
		\node[align=center] at (10,-4.5) {5.2};
		\draw (8.5,-3) -- (8.5,-3.5);

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {1.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {12\\9.2};
		\node[align=center] at (14,-7) {2.0};
